Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-07-19 edubots_surveys.Rnw
minor fixes

% Add something about intro
% RQ1 discussion about messaging app: they consider a IM the Moodle messaging
% Olia: it's not so easy to change habits, even in the case of major crisis. - JJ
% Relationship between changes, gender and discipline (Olia) - JJ
% 
Our initial intention in the design of these surveys was to probe the opinions of tertiary education teachers in the introduction of chatbot technologies in the class. We wanted to find the answer to four research questions, of which the first was to check whether teachers already used some kind of messaging application, and the one they preferred. Depending on the answer, different technologies could be (or not) available for the introduction of chatbots. In this case, the design of the survey introduced some ambiguity on what we really consider "messaging technology", that was eventually resolved by the answers; apparently, anything that sends messages (even if they are not instant, even if they don't have a dedicated application) was the concept in the mind of the surveyed.

Additionally, the question on COVID reflected the big challenge that represents changing habits, even in the case of a major crisis. Very few people actually changed, with women vs. men being an exception, as well as those teaching social sciences standing out among the rest. We don't have any kind of explanation for this behavior, other than technologies are perceived, and adopted, in a different depending on background and, apparently, gender.

>>>>

% Add something about intro
% RQ1 discussion about messaging app: they consider a IM the Moodle messaging
% Olia: it's not so easy to change habits, even in the case of major crisis. - JJ
% Relationship between changes, gender and discipline (Olia) - JJ
% 
Our initial intention in the design of these surveys was to probe the opinions of tertiary education teachers in the introduction of chatbot technologies in class. We wanted to find the answer to four research questions, of which the first was to check whether teachers already used some kind of messaging application, and the one they preferred. Depending on the answer, different technologies could be (or not) available for the introduction of chatbots. In this case, the design of the survey introduced some ambiguity on what we really consider "messaging technology", that was eventually resolved by the answers; apparently, anything that sends messages (even if they are not instant, even if they do not have a dedicated application) was the concept in the mind of the surveyed.

Additionally, the question on COVID reflected the big challenge that represents changing habits, even in the case of a major crisis. Very few people actually changed, with women vs. men being an exception, as well as those teaching social sciences standing out among the rest. We do not have any kind of explanation for this behavior, other than technologies are perceived, and adopted, in a different way depending on background and, apparently, gender.
